### 2020-01-02 results/sec_2-work_load.tex
Work plan - Data preparation

> Then using those, create timeseries metadata (how it assure 10% of Grid data)
In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \say{randomised} - create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time. - https://jmeter.apache.org/usermanual/best-practices.html\#lean_mean}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \ref{se:test_plan}.
Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}. This is occurred in the setup phase of the test cases. The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

@@

> Then how water level data for Grid time series created
Almost similar to how was the precipitation data proceed, the water level are prepared for Grid data. One exception with Grid data during this test cases was, the maximum time step is 30min, instead of 15min due to larger size of the data. But the \acrshort{wdias} is capable of supporting such request. The main purpose of the \acrshort{wdias} is to provide a extensible architecture framework, during the performance testing it is not much consider about scaling the Grid data handling as it using \acrshort{netcdf}, and it is another domain with an attraction up to some extend.

\begin{lstlisting}[language=sh, caption=Water level Data Preparation]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_water-level.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_water-level.sh prepare
    Segregate single file data into multiple grid file dirs based on date. And Separate into main dirs of 15min, 30min, 60min and create tar files
  setup_water-level.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_water-level.sh cleanup
    Clean up extracted dirs
\end{lstlisting}
The water level also contains the real data for one month of period, and \emph{setup\_waterlevel.sh} script provide the functionality of prepare, cleanup and extract.
Also it reset and repeat reading from the beginning when the \acrshort{jmeter} date counter keep increasing.

> Talk about the test test up - JMeter
 -> mentioned distributed setup test data collect issue and continue with one server coz it can support what is required
> Talk about Stepping timer with concurrent thread group
> Add screenshot of jmeter setup
> Add prod req graph
> talk about how test cases are enabled
> talk about test plans can run
\begin{lstlisting}[language=sh, caption=Test Plan Help]
-h | --help: Usage
    <ROOT_DIR> <COMMAND> <REQ_SIZE>
    - REQ_SIZE (optional): 24(1) | 288(2) | 1044(3)
  NOTE: Modify test.conf as necessary
  e.g.
  test_plan.sh ~/wdias/wdias-performance-test run
  test_plan.sh ~/wdias/wdias-performance-test run 2
  - Run all the steps in order of setup, import, 
    create_extension, extension, export, all, query

>>>>

> Then using those, create timeseries metadata (how it assure 10% of Grid data)
In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time. jmeter best practices lean\_mean}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \ref{se:test_plan}.
Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}. This is occurred in the setup phase of the test cases. The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

@@

> Then how water level data for Grid time series created
Almost similar to how was the precipitation data proceed, the water level are prepared for Grid data. One exception with Grid data during this test cases was, the maximum time step is 30min, instead of 15min due to larger size of the data. But the \acrshort{wdias} is capable of supporting such request. The main purpose of the \acrshort{wdias} is to provide a extensible architecture framework, during the performance testing it is not much consider about scaling the Grid data handling as it using \acrshort{netCDF}, and it is another domain with an attraction up to some extend.

\begin{lstlisting}[language=sh, caption=Water level Data Preparation]
Set ROOT_DIR=~/wdias/wdias-performance-test
-h | --help: Usage
  setup_water-level.sh  <COMMAND>
    - COMMAND: help | extract | prepare | cleanup | populate
  e.g.
  setup_water-level.sh prepare
    Segregate single file data into multiple grid file directories based on date. And Separate into main directories of 15min, 30min, 60min and create tar files
  setup_water-level.sh extract
    Extract the tar files into 15min, 30min and 60min
  setup_water-level.sh cleanup
    Clean up extracted directories
\end{lstlisting}
The water level also contains the real data for one month of period, and \emph{setup\_waterlevel.sh} script provide the functionality of prepare, cleanup and extract.
Also it reset and repeat reading from the beginning when the \acrshort{jmeter} date counter keep increasing.

> Talk about the test test up - JMeter
 -> mentioned distributed setup test data collect issue and continue with one server coz it can support what is required
\subsection{Experimental Setup}
In order to create higher work load using the \acrshort{jmeter}, it has Distributed Testing feature. It is using the master slave approach and it allowed to handle all the test cases via single instance, rather handling separate instances. But it has following limitation;
\say{Note: The same test plan is run by all the servers. JMeter does not distribute the load between servers, each runs the full test plan. So if you set 1000 Threads and have 6 JMeter server, you end up injecting 6000 Threads.}

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{results/work_load/experimental_setup_v3.jpg}
    \caption{Experimental Setup with JMeter}
    \label{fi:experimental_setup}
\end{figure}
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{Weather Data Integration and Assimilation System Architecture for Handle Request Asynchronously}
    \label{fi:wdias_micro_async}
\end{figure}

> Talk about Stepping timer with concurrent thread group

> Add screenshot of jmeter setup
> Add prod req graph
> talk about how test cases are enabled
> talk about test plans can run
\begin{lstlisting}[language=sh, caption=Test Plan Help]
-h | --help: Usage
    <ROOT_DIR> <COMMAND> <REQ_SIZE>
    - REQ_SIZE (optional): 24(1) | 288(2) | 1044(3)
  NOTE: Modify test.conf as necessary
  e.g.
  test_plan.sh ~/wdias/wdias-performance-test run
  test_plan.sh ~/wdias/wdias-performance-test run 2
  - Run all the steps in order of setup, import, 
    create_extension, extension, export, all, query
